A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
spell check

### Disease presure factor
We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure. We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot. 
We will create two categories, `lowD` and `highD`. 
We will use the median `AUDPC` to separate the trials into these two groups.

@@

Lets have a quick look to examine weather trials with high disease pressure sustain a greater yield loss.

```{r plot_disease_pressure}
slimmer_PM_dat %>%
   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
   geom_boxplot()

slimmer_PM_dat[is.na(slimmer_PM_dat$D_pres),]
```

@@

We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
Fow now lets assign the most used row spacing of 0.33
```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33

>>>>

### Disease pressure factor
We may wish to investigate the impact of spray management in mitigating the yield loss through the effect on the disease pressure. We will set a categorical variable to indicate the amount of disease pressure in the trial, which will be evaluated on the control plot. 
We will create two categories, `lowD` and `highD`. 
We will use the median `AUDPC` to separate the trials into these two groups.

@@

Lets have a quick look to examine whether trials with high disease pressure sustain a greater yield loss.

```{r plot_disease_pressure}
slimmer_PM_dat %>%
   ggplot(aes(x = D_pres, y = grain_yield.t.ha))+
   geom_boxplot()
```

@@

We may want to consider row spacing in the trials, However one of the locations has NA as the row spacing. 
For now lets assign the most used row spacing of 0.33
```{r}
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),]
slimmer_PM_dat[is.na(slimmer_PM_dat$row_spacing),"row_spacing"] <- 0.33
